---
output:
  github_document:
    toc: true
    toc_depth: 2
---

rfutbin
=================

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

rfutbin: Search prices for FIFA Ultimate Team players in Futbin webpage

## Installation

This package is currently available only on GitHub. To install it, use the
`devtools` package:

```{r eval = FALSE}
library(devtools)
install_github("danielredondo/rfutbin")
```

## Usage

There's just one exported function in this package, `futbin_search`. It has the following parameters:

- `name`. Optional. Name of the player. If leaved blank, it will report the 30 highest-rated players of the game.

- `version`. Optional. Version of the card. It can be "Normal", "CL" (Champions League), "IF" (In-Form), "SIF" (Second In-Form), ...

- `messages`. Optional. To show additional messages (webpage used and number of players found).

The output of the function is a dataframe with all the players found searching for `name` and  `version`.

## Examples

```{r}
library(rfutbin)
```

```{r}
futbin_search("Lionel Messi")
```

```{r}
futbin_search("Lionel Messi", version = "Normal")
```

```{r}
futbin_search("Luka Modric", version = "IF", messages = TRUE)
```
